### 2024-12-09 Draft1.tex
Final touches

The method of Calculus cryptography that I will be using in my comparison utilizes  differential equations as encryption mechanisms. A simple example involves encoding information as the solution to a specific differential equation. The sender encodes a message \( M \) by creating a differential equation where \( M \) is embedded within the boundary or initial conditions. For example:

@@

>>>>

The method of Calculus cryptography that I will be using in my comparison utilizes differential equations as encryption mechanisms. A simple example involves encoding information as the solution to a specific differential equation \cite{bhardwaj2014calculus}. The sender encodes a message \( M \) by creating a differential equation where \( M \) is embedded within the boundary or initial conditions. For example:

@@

\bibitem{bhardwaj2014calculus}
Bhardwaj, C.R.S. "Calculus Cryptography." \textit{International Journal of Scientific Research}, vol. 3, no. 2, 2014, pp. 308--309. \url{https://www.worldwidejournals.com/international-journal-of-scientific-research-(IJSR)/recent_issues_pdf/2014/February/February_2014_1391507412_0c336_97.pdf}.
